---
title: "Data Analysis Shiny App"
author: "Mohamed BELMOUIDI"
date: "December 31, 2024"
output: ioslides_presentation
runtime: shiny
---

  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
```

## The Problem

Ever wondered how to quickly analyze numeric data?
  
- Many people struggle with basic data analysis
- Excel can be cumbersome
- Statistical software can be overwhelming
- Need for a simple, user-friendly solution

## Our Solution {.build}

Introducing the Data Analysis Shiny App!
  
```{r, echo=TRUE}
# Example of how simple the analysis can be
sample_data <- c(1, 2, 3, 4, 5)
cat("Basic Statistics:\n")
cat("Mean:", mean(sample_data), "\n")
cat("Median:", median(sample_data), "\n")
cat("SD:", sd(sample_data), "\n")
```

## Features in Action

```{r, fig.height=4}
# Generate sample data for demonstration
set.seed(123)
demo_data <- rnorm(100)

# Create a histogram
ggplot(data.frame(x=demo_data), aes(x=x)) +
  geom_histogram(fill="lightblue", color="white") +
  theme_minimal() +
  labs(title="Example Visualization",
       x="Value",
       y="Count")
```

## Try It Yourself!

**Why Choose Our App?**
- Simple interface
- Instant results
- Visual insights
- Perfect for beginners

Visit: [https://belmouidi-learning-journey.shinyapps.io/my_shiny_app/]

Source code: [https://github.com/Mohamed-BELMOUIDI/Shiny-application]
